New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-04 Manuscript/Manuscript.Rmd

@@

Subsection text here.

### Subsubsection Heading Here

>>>>

The objective of this work is twofold: 1) estimate the interaction strength of the Weddell Sea food web, and 2) 
determine key trophic species considering its influence on the stability of the network.

@@

The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km.
Water depth varies from 200 to 500 m. Shallower areas are covered by continental ice, which forms the coastline
along the eastern and southern part of the Weddell Sea. The shelf area contains a complex three-dimensional
habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and
a spatially patchy distribution of organisms [@Dayton1990, @Teixido2002].

## Data source
